Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-10-13 paper/sections/discussion.tex
[ paper ] reviewed to resolve section.

\textit{Splitting}. To prove a goal, \Metis splits the goal into
disjoint cases. This process produces a list of new subgoals, the
conjunction of these subgoals implies the goal. Then, a proof of the
goal becomes in smaller proofs, one refutation for each subgoal.
These subgoals are introduced in the \TSTP derivation with the \strip
inference rule. We refer the reader to see Section~\ref{sssec:splitting-goal} for the formalization of \strip rule.

@@

\textit{Resolution.} The \resolve rule incorporates  the resolution theorem showed in Fig.~\ref{fig:metis-inferences} with
three arguments: a positive literal $l$ to apply the resolution theorem, and two derivations, $\mathcal{D}₁$ and $\mathcal{D}₂$.

The positive literal $l$ must occur in
the formula from the first derivation $\mathcal{D}₁$, and the
negative literal must occur in the formula from the second derivation $\mathcal{D}₂$ (see the pattern in \Metis' logic core for the \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}).
We refer the reader to see Section~\ref{sssec:resolve} for the formalization of the \resolve rule.

>>>>

\textit{Splitting}. To prove a goal, \Metis splits the goal into
disjoint cases. This process produces a list of new subgoals, the
conjunction of these subgoals implies the goal. Then, a proof of the
goal becomes in smaller proofs, one refutation for each subgoal.
These subgoals are introduced in the \TSTP derivation with the \strip
inference rule. We refer the reader to see Section~\ref{sssec:strip-a-goal} for the formalization of \strip rule.

@@

\textit{Resolution.} The \resolve rule incorporates the resolution theorem showed in Fig.~\ref{fig:metis-inferences} for the \TSTP derivations.
This rule posses three arguments: a positive literal $l$ to apply the resolution theorem, and two derivations, $\mathcal{D}₁$ and $\mathcal{D}₂$.

The positive literal $l$ must occur in
the formula from the first derivation $\mathcal{D}₁$, and the
negative literal must occur in the formula from the second derivation $\mathcal{D}₂$ (see the pattern in the \emph{resolve} rule).
We refer the reader to see Section~\ref{sssec:resolve} for the formalization of the \resolve rule.

### 2017-10-13 paper/sections/metis-language-and-proofs.tex
[ paper ] reviewed to resolve section.

For instance, let us express the problem
$p\, \vdash \neg (p \wedge \neg p) ∨ (q \wedge \neg q)$
in \TPTP syntax. We begin by declaring the $p$ axiom using the keyword,
\verb!axiom!. Later, we include the expected conclusion using the \verb!conjecture! keyword.

@@

Since the scope of the problems treated in this research is CPL, from the list of \Metis inference rules in~\ref{fig:metis-inferences}, we found that only three rules apply: \emph{axiom}, \emph{assume} and \emph{resolve} rule.
Nonetheless, \TSTP derivations replied by \Metis use other rules. They are \canonicalize, \clausify, \conjunct, \simplify, \negate, and
\strip.

>>>>

For instance, let us express the problem
$p\, \vdash \neg (p \wedge \neg p) ∨ (q \wedge \neg q)$
in \TPTP syntax. We begin by declaring the $p$ axiom using the \verb!axiom!
keyword. Later, we include the expected conclusion using the \verb!conjecture! keyword.

@@

Since the scope of the problems treated in this research is \CPL, from the list of \Metis inference rules in Fig.~\ref{fig:metis-inferences}, we found that only three rules apply: \emph{axiom}, \emph{assume} and \emph{resolve} rule.
Nonetheless, \TSTP derivations replied by \Metis use other rules. They are \canonicalize, \clausify, \conjunct, \simplify, \negate, and
\strip.
